HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
section 4

We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
\end{inparadesc}

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to be reviewed\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved.}

Here is \XXX{another} example with a missing linker: the source \equo{However,
this review\dots} was translated as \equo{Diese
\"Uberpr\"ufung\dots} (lit. \equo{This review}). The omission is not by HMEANT at
all.

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
The coverage of
these and other phenomena by HUME will allow to determine empirically
(rather than stipulate), which semantic structures are important
to preserve for MT evaluation, and which are less important.

@@

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign it a very low score,
as it failed to translate the main verb.

@@

In HMEANT, the alignment between the (reference and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and candidate
translations diverge without any good reason, for instance due to a different
interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations also at the alignment stage
to avoid unduly penalization due to such a spurious divergence.
The same issue was observed by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

HUME uses only automatic (word-level) alignment, which only serves as a cue for directing
the attention of the annotators.
The user is expected to mentally correct the alignment as needed.

>>>>

We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to review\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved.}

Another example where a linker is omitted in translation:
the source \equo{However, this review\dots}, which was translated as \equo{Diese
\"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all.

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
The coverage of
these and other phenomena by HUME will allow to empirically determine 
(rather than stipulate), which semantic structures are important
to preserve for MT evaluation, and which are less important.

@@

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

@@

In HMEANT, the alignment between the (reference and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and of an accurate translation
still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations at the alignment stage,
to avoid unduly penalization due to such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue was observed by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

%HUME uses only automatic (word-level) alignment, which only serves as a cue for directing
%the attention of the annotators.
%The user is expected to mentally correct the alignment as needed.
HUME uses automatic (word-level) alignment, which only
serves as a cue for directing the attention of the annotators.
The user is expected to mentally correct the
alignment as needed, thus circumventing this difficulty.
